---
title: "R Experiments - Working"
output: html_notebook
---

Stats Function
```{r,include = FALSE}
# Statistics
my.stat <- function(k.pred, gen.pred, true.label){
  k = length(k.pred)
  #Majority <- mode(k.pred)                     # Classifiers
  
  # Best k model
  SSE.k <- numeric(k)
  for(j in 1:k){
    SSE.k[j] <- sum((k.pred[,j] - true.label)^2)
  }
  MSE_best <- min(SSE.k)/length(true.label)
  
  # Averaged Stats from k models
  Avg.pred <- rowMeans(k.pred)
  SSE <- sum((Avg.pred - true.label)^2)
  MSE_avg <- SSE/length(true.label)
  
  # SG stats
  SSE <- sum((gen.pred - true.label)^2)
  MSE_SG <- SSE/length(true.label)
  
  return(c(MSE_best, MSE_avg, MSE_SG))
}
```

Data Import
```{r, include = FALSE}
#source('./functions/SG.R') # Not sure why this isn't working
setwd('./functions')
#getwd()
source('./SG.R')            # Seems to work, once setwd(./functions)
library(ggplot2)
library(rmutil)

#library(parallel)
#no_cores <- detectCores()-1
#cl <- makeCluster(no_cores) # library(parallel)
# FUNCTION GOES HERE
#stopCluster(cl)
```

Data Generation
```{r, inlude = FALSE}
n = 100
sigma = 1
tr.data <- data_gen(n, d, p, true_model, sigma)
res <- SG(n, d = 1, p = 1, sigma = 10, true.model, tr.data)
res[[3]] = tr.data$X

ggplot(tr.data,aes(X)) +
  geom_line(aes(y=Yt,colour="Gen Function")) +
  geom_point(aes(y=Ye,colour="Data")) + 
  geom_line(aes(y=res[[1]][[2]],colour="SG Fit")) + 
  labs(x = "X", y = "Y", title = "Train data")+ theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("SG Fit" = "green", "Data" = "black", "Gen Function" = "red"))
```


**Sample Size  5 to 90**

**Replicates   100**

This function $3x^2 + x + 5$ is used to generate the data, with noise from N(0, $\sigma = 1$)

Training Models used: $\begin{bmatrix} x^3 & & &  \\ x^3 & x^4 & &  \\ x^3 & x^4& x^5 \\ ...&&&\\x^3 & x^4&...&...x^{32}\end{bmatrix}$ based on the R function lm($Y \sim row_i$ )



# With LOO (Grunwald)
```{r, echo = FALSE}
# aX^2 + bX + c
true_model <- function(input, p = 1){
    
    coff = c(3, 1, 5) # (aX^2, bX, c)
    ans = coff[1] * (input^2) + coff[2] * input + coff[3]
    return(ans)
}

set.seed(9)

param.min = 5
param.max = 175
replicate = 50
iter = 5
d = 1
p = 1
k = 10
sigma = 1

res <- rep(list(), 3) 

tr.param_MSE <- data.frame("SampleSize" = param.min:param.max , "SG Model" = 0)
te.param_MSE <- data.frame("SampleSize" = param.min:param.max , "SG Model" = 0)
true.Model.MSE <- data.frame("SampleSize" = param.min:param.max , "True Model" = 0)
dg.MSE       <- data.frame("SampleSize" = param.min:param.max , "True Model" = 0)

for(param in seq(1,(param.max - param.min + 1),iter) ) {

  tr.ans <- rep(0, replicate)
  te.ans <- rep(0, replicate)
  dg.ans <- numeric(replicate)
  true.model.ans <- numeric(replicate)
  
  n = param.min + param - 1
  
  for(j in 1: replicate){
    # make data
    tr.data <- data_gen(n, d, p, true_model, sigma)
    res <- SG(n, d = 1, p = 1, k, sigma = 1, true_model, tr.data)
    
    tr.ans[j] <- sum(( (res[[1]][[2]] - res[[1]][[3]])^2) /length(res[[1]][[3]]))
    te.ans[j] <- sum(( (res[[2]][[2]] - res[[2]][[3]])^2) /length(res[[2]][[3]]))
    
    dg.ans[j] <- 1/n * sum((tr.data$Ye - tr.data$Yt)^2) # MSE of train data
    
    ## Actual Best Model
    coff <- lm(tr.data$Ye ~ tr.data$X + I((tr.data$X)^2))$coefficients
    true.pred <- coff[1] + coff[2] * (tr.data$X) + coff[3] * (tr.data$X)^2
    true.model.ans[j] <- 1/n * sum((true.pred - tr.data$Ye)^2) # MSE of train data
    
  }
  tr.param_MSE[param,2] <- mean(tr.ans)
  te.param_MSE[param,2] <- mean(te.ans)
  dg.MSE[param,2]       <- mean(dg.ans)
  true.Model.MSE[param,2] <- mean(true.model.ans)
  
    
  cat(" ",param.max + 1 - param)
}

# Remove skipped elements (eg when Sample Size = 5,10,15,20...)
include = seq(1,(param.max - param.min + 1),iter)
tr.param_MSE = tr.param_MSE[include,]
te.param_MSE = te.param_MSE[include,]
dg.MSE     = dg.MSE[include,]
true.Model.MSE = true.Model.MSE[include,]


MSEs_LOO = data.frame(SampleSize = dg.MSE$SampleSize, 
                  tr = tr.param_MSE, 
                  te = te.param_MSE, 
                  True.Model = true.Model.MSE$True.Model,
                  dg.Model = dg.MSE$True.Model)
```


```{r, echo = FALSE}
ggplot(MSEs_LOO,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size",title = "Grunwald with LOO") + theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))

ggplot(MSEs_LOO,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size", title = "Grunwald with LOO: ZOOMED") + ylim(0.1,15) +
  theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))

ggplot(MSEs_LOO,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size", title = "Grunwald with LOO: ZOOMED") + ylim(0.1,2.5) +
  theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))
```


```{r, include = FALSE}
Diff = data.frame(Difference = MSEs$te.SG.Model - MSEs$tr.SG.Model, SampleSize = MSEs$SampleSize)
ggplot(Diff,aes(SampleSize)) + 
  geom_line(aes(y=Difference,colour="Difference")) +
  labs(y = "MSE",x="Sample Size",title = "MSE Difference Between Training and Testing") + theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Difference" = "black"))

ggplot(Diff,aes(SampleSize)) + 
  geom_line(aes(y=Difference),colour="black") +
  labs(y = "MSE",x="Sample Size",title = "MSE Difference Between Training and Testing: ZOOMED") + 
  theme(legend.position = "bottom") + ylim(-0.1,quantile(p = 0.95,Diff$Difference))
```

# Without LOO (Grunwald)
```{r, echo = FALSE}
# aX^2 + bX + c
true_model <- function(input, p = 1){
    
    coff = c(3, 1, 5) # (aX^2, bX, c)
    ans = coff[1] * (input^2) + coff[2] * input + coff[3]
    return(ans)
}

########################################
# Program Runs From Here!!
########################################

set.seed(9)

param.min = 5
param.max = 175
replicate = 50
iter = 5
d = 1
p = 1
k = 10
sigma = 1

res <- rep(list(), 3) 

tr.param_MSE <- data.frame("SampleSize" = param.min:param.max , "SG Model" = 0)
te.param_MSE <- data.frame("SampleSize" = param.min:param.max , "SG Model" = 0)
true.Model.MSE <- data.frame("SampleSize" = param.min:param.max , "True Model" = 0)
dg.MSE       <- data.frame("SampleSize" = param.min:param.max , "True Model" = 0)

for(param in seq(1,(param.max - param.min + 1),iter) ) {

  tr.ans <- rep(0,replicate)
  te.ans <- rep(0,replicate)
  dg.ans <- numeric(replicate)
  true.model.ans <- numeric(replicate)
  
  n = param.min + param - 1
  
  for(r in 1: replicate){
    # make data
    tr.data <- data_gen(n, d, p, true_model, sigma)
    te.data <- data_gen(1000, d, p, true_model, sigma)
    
    ## Train k - models +  Stacked Generalizer
    pred <- train_predict_all(tr.data,generate = FALSE, d,p, k, sigma)
    SG.weights <- generalize(pred[,1:k], pred$Ye, k)
    
    # Predict Train
    tr.SG.pred <- numeric( nrow( tr.data))

    for(i in 1:nrow(tr.data)){
      for(j in 1:k){
        tr.SG.pred[i] = tr.SG.pred[i] + SG.weights[j] * pred[i,j]
      }
    }
    
    # Predict Test
    te.SG.pred <- numeric( nrow( te.data))
    
    pred <- matrix(ncol = k, nrow = nrow(te.data) )
    FUN  <- legendre.polynomials(k+2)
    for(i in 1:k){
    
      train <- matrix(0, nrow = nrow(tr.data), ncol = i)
      test  <- matrix(0, nrow = nrow(te.data), ncol = i)
    
      for(j in 1:i){
        train[,j] <- predict(FUN[[j+2]], tr.data$X)
        test[,j]  <- predict(FUN[[j+2]], te.data$X) 
      }
    
      coeff  <- lm(tr.data$Ye ~ ., data = data.frame(train))$coefficients
      coeff[is.na(coeff)] = 0
    
    
      pred[,i]   = coeff[1]
      for(j in 1:i)
        pred[,i] = pred[,i] + coeff[i+1] * test[,i]
    }
    
    pred = data.frame(pred, Ye = te.data$Yt)
    
    for(i in 1:nrow(te.data)){
      for(j in 1:k){
        te.SG.pred[i] = te.SG.pred[i] + SG.weights[j] * pred[i,j]
      }
    }
    
    tr.ans[r] <- sum(( (tr.SG.pred - tr.data$Ye)^2) /length(tr.data$Ye))
    te.ans[r] <- sum(( (te.SG.pred - te.data$Ye)^2) /length(te.data$Ye))
    
    dg.ans[r] <- 1/n * sum((tr.data$Ye - tr.data$Yt)^2) # MSE of train data
    
    ## Actual Best Model
    coff <- lm(tr.data$Ye ~ tr.data$X + I((tr.data$X)^2))$coefficients
    true.pred <- coff[1] + coff[2] * (tr.data$X) + coff[3] * (tr.data$X)^2
    true.model.ans[r] <- 1/n * sum((true.pred - tr.data$Ye)^2) # MSE of train data
    
  }
  tr.param_MSE[param,2] <- mean(tr.ans)
  te.param_MSE[param,2] <- mean(te.ans)
  dg.MSE[param,2]       <- mean(dg.ans)
  true.Model.MSE[param,2] <- mean(true.model.ans)
  
    
  cat(" ",param.max + 1 - param)
}

include = seq(1,(param.max - param.min + 1),iter)
tr.param_MSE = tr.param_MSE[include,]
te.param_MSE = te.param_MSE[include,]
dg.MSE     = dg.MSE[include,]
true.Model.MSE = true.Model.MSE[include,]

MSEs_wo_LOO = data.frame(SampleSize = dg.MSE$SampleSize, 
                  tr = tr.param_MSE, 
                  te = te.param_MSE, 
                  True.Model = true.Model.MSE$True.Model,
                  dg.Model = dg.MSE$True.Model)
```


```{r, echo = FALSE}
ggplot(MSEs_wo_LOO,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size",title = "Grunwald without LOO") + theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))

ggplot(MSEs_wo_LOO,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size", title = "Grunwald without LOO: ZOOMED") + ylim(0.1,15) +
  theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))

ggplot(MSEs_wo_LOO,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size", title = "Grunwald without LOO : ZOOMED") + ylim(0.1,2.5) +
  theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))
```


```{r, inlude = FALSE}
Diff = data.frame(Difference = MSEs$te.SG.Model - MSEs$tr.SG.Model, SampleSize = MSEs$SampleSize)
ggplot(Diff,aes(SampleSize)) + 
  geom_line(aes(y=Difference,colour="Difference")) +
  labs(y = "MSE",x="Sample Size",title = "MSE Difference Between Training and Testing") + theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Difference" = "black"))

ggplot(Diff,aes(SampleSize)) + 
  geom_line(aes(y=Difference),colour="black") +
  labs(y = "MSE",x="Sample Size",title = "MSE Difference Between Training and Testing: ZOOMED") + 
  theme(legend.position = "bottom") + ylim(-0.1,quantile(p = 0.95,Diff$Difference))
```


# Without LOO + DP x 2

$\epsilon = 0.01$ also tried $\epsilon=\dfrac{\sigma^2}{n}$
```{r, echo = FALSE}
# aX^2 + bX + c
true_model <- function(input, p = 1){
    
    coff = c(3, 1, 5) # (aX^2, bX, c)
    ans = coff[1] * (input^2) + coff[2] * input + coff[3]
    return(ans)
}

########################################
# Program Runs From Here!!
########################################

set.seed(9)

param.min = 5
param.max = 80
replicate = 100
iter = 5
d = 1
p = 1
k = 4
sigma = 1

res <- rep(list(), 3) 

tr.param_MSE <- data.frame("SampleSize" = param.min:param.max , "SG Model" = 0)
te.param_MSE <- data.frame("SampleSize" = param.min:param.max , "SG Model" = 0)
true.Model.MSE <- data.frame("SampleSize" = param.min:param.max , "True Model" = 0)
dg.MSE       <- data.frame("SampleSize" = param.min:param.max , "True Model" = 0)

for(param in seq(1,(param.max - param.min + 1),iter) ) {

  tr.ans <- rep(0,replicate)
  te.ans <- rep(0,replicate)
  dg.ans <- numeric(replicate)
  true.model.ans <- numeric(replicate)
  
  n = param.min + param - 1
  
  for(r in 1: replicate){
    # make data
    tr.data <- data_gen(n, d, p, true_model, sigma)
    te.data <- data_gen(1000, d, p, true_model, sigma)
      
    DP_noise_1 = rlaplace(n,0,sigma/100)    # Addition of Laplace Noise
    DP_noise_2 = rlaplace(n,0,sigma/100)    # Addition of Laplace Noise
    
    ## Train k - models +  Stacked Generalizer
    # Add Noise 1
    model <- rep(list(),k)
    for(i in 1:k){
      model[[i]] <- lm(tr.data$Ye ~ I((tr.data$X + DP_noise_1)^(i+2)))
    }
    
    # Add Noise 2
    pred <- data.frame(matrix(ncol = k, nrow = nrow(tr.data) ) )
    for(i in 1:k){
      pred[,i] = model[[i]]$coefficients[1] + model[[i]]$coefficients[2] * (tr.data$X + DP_noise_2)^(i+2)
    }
    pred = data.frame(pred, Ye = tr.data$Ye)
    
    SG.weights <- generalize(pred[,1:k], pred$Ye, k)
    
    # Predict
    tr.SG.pred <- numeric( nrow( tr.data))
    te.SG.pred <- numeric( nrow( te.data))

    for(i in 1:nrow(tr.data)){
      for(j in 1:k){
        tr.SG.pred[i] = tr.SG.pred[i] + SG.weights[j] * pred[i,j]
      }
    }
  
    pred <- matrix(ncol = k, nrow = nrow(te.data) )
    
    for(i in 1:k){
      pred[,i]   = model[[i]]$coefficients[1] + model[[i]]$coefficients[2] * te.data[,1:d]^(i+2)  
    }
    pred = data.frame(pred, Ye = te.data$Yt)
    
    for(i in 1:nrow(te.data)){
      for(j in 1:k){
        te.SG.pred[i] = te.SG.pred[i] + SG.weights[j] * pred[i,j]
      }
    }
    
    tr.ans[r] <- sum(( (tr.SG.pred - tr.data$Ye)^2) /length(tr.data$Ye))
    te.ans[r] <- sum(( (te.SG.pred - te.data$Ye)^2) /length(te.data$Ye))
    
    dg.ans[r] <- 1/n * sum((tr.data$Ye - tr.data$Yt)^2) # MSE of train data
    
    ## Actual Best Model
    coff <- lm(tr.data$Ye ~ tr.data$X + I((tr.data$X)^2))$coefficients
    true.pred <- coff[1] + coff[2] * (tr.data$X) + coff[3] * (tr.data$X)^2
    true.model.ans[r] <- 1/n * sum((true.pred - tr.data$Ye)^2) # MSE of train data
    
  }
  tr.param_MSE[param,2] <- mean(tr.ans)
  te.param_MSE[param,2] <- mean(te.ans)
  dg.MSE[param,2]       <- mean(dg.ans)
  true.Model.MSE[param,2] <- mean(true.model.ans)
  
    
  cat(" ",param.max + 1 - param)
}

# Remove skipped elements (eg when Sample Size = 5,10,15,20...)
include = seq(1,(param.max - param.min + 1),iter)
tr.param_MSE = tr.param_MSE[include,]
te.param_MSE = te.param_MSE[include,]
dg.MSE     = dg.MSE[include,]
true.Model.MSE = true.Model.MSE[include,]

MSEs_wo_LOO_DP = data.frame(SampleSize = dg.MSE$SampleSize, 
                  tr = tr.param_MSE, 
                  te = te.param_MSE, 
                  True.Model = true.Model.MSE$True.Model,
                  dg.Model = dg.MSE$True.Model)
```


```{r, echo = FALSE}
ggplot(MSEs_wo_LOO_DP,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size",title = "MSE") + theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))

ggplot(MSEs_wo_LOO_DP,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size", title = "MSE : ZOOMED") + ylim(0.1,15) +
  theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))

ggplot(MSEs_wo_LOO_DP,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size", title = "MSE : ZOOMED") + ylim(0.1,2.5) +
  theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))
```

# Without LOO + DP x k

$\epsilon = 0.01$ also tried $\epsilon=\dfrac{\sigma^2}{n}$
```{r, echo = FALSE}
# aX^2 + bX + c
true_model <- function(input, p = 1){
    
    coff = c(3, 1, 5) # (aX^2, bX, c)
    ans = coff[1] * (input^2) + coff[2] * input + coff[3]
    return(ans)
}

########################################
# Program Runs From Here!!
########################################

set.seed(9)

param.min = 5
param.max = 80
replicate = 100
iter = 5
d = 1
p = 1
k = 4
sigma = 1

res <- rep(list(), 3) 

tr.param_MSE <- data.frame("SampleSize" = param.min:param.max , "SG Model" = 0)
te.param_MSE <- data.frame("SampleSize" = param.min:param.max , "SG Model" = 0)
true.Model.MSE <- data.frame("SampleSize" = param.min:param.max , "True Model" = 0)
dg.MSE       <- data.frame("SampleSize" = param.min:param.max , "True Model" = 0)

for(param in seq(1,(param.max - param.min + 1),iter) ) {

  tr.ans <- rep(0,replicate)
  te.ans <- rep(0,replicate)
  dg.ans <- numeric(replicate)
  true.model.ans <- numeric(replicate)
  
  n = param.min + param - 1
  
  for(r in 1: replicate){
    # make data
    tr.data <- data_gen(n, d, p, true_model, sigma)
    te.data <- data_gen(1000, d, p, true_model, sigma)
      
    ## Train k - models +  Stacked Generalizer
    model <- rep(list(),k)
    for(i in 1:k){
      DP_noise_k = rlaplace(n,0,sigma/100)
      model[[i]] <- lm(tr.data$Ye ~ I((tr.data$X + DP_noise_k)^(i+2)))
    }
    
    pred <- data.frame(matrix(ncol = k, nrow = nrow(tr.data) ) )
    for(i in 1:k){
      pred[,i] = model[[i]]$coefficients[1] + model[[i]]$coefficients[2] * (tr.data$X)^(i+2)
    }
    pred = data.frame(pred, Ye = tr.data$Ye)
    
    SG.weights <- generalize(pred[,1:k], pred$Ye, k)
    
    # Predict
    tr.SG.pred <- numeric( nrow( tr.data))
    te.SG.pred <- numeric( nrow( te.data))

    for(i in 1:nrow(tr.data)){
      for(j in 1:k){
        tr.SG.pred[i] = tr.SG.pred[i] + SG.weights[j] * pred[i,j]
      }
    }
  
    pred <- matrix(ncol = k, nrow = nrow(te.data) )
    
    for(i in 1:k){
      pred[,i]   = model[[i]]$coefficients[1] + model[[i]]$coefficients[2] * te.data[,1:d]^(i+2)  
    }
    pred = data.frame(pred, Ye = te.data$Yt)
    
    for(i in 1:nrow(te.data)){
      for(j in 1:k){
        te.SG.pred[i] = te.SG.pred[i] + SG.weights[j] * pred[i,j]
      }
    }
    
    tr.ans[r] <- sum(( (tr.SG.pred - tr.data$Ye)^2) /length(tr.data$Ye))
    te.ans[r] <- sum(( (te.SG.pred - te.data$Ye)^2) /length(te.data$Ye))
    
    dg.ans[r] <- 1/n * sum((tr.data$Ye - tr.data$Yt)^2) # MSE of train data
    
    ## Actual Best Model
    coff <- lm(tr.data$Ye ~ tr.data$X + I((tr.data$X)^2))$coefficients
    true.pred <- coff[1] + coff[2] * (tr.data$X) + coff[3] * (tr.data$X)^2
    true.model.ans[r] <- 1/n * sum((true.pred - tr.data$Ye)^2) # MSE of train data
    
  }
  tr.param_MSE[param,2] <- mean(tr.ans)
  te.param_MSE[param,2] <- mean(te.ans)
  dg.MSE[param,2]       <- mean(dg.ans)
  true.Model.MSE[param,2] <- mean(true.model.ans)
  
    
  cat(" ",param.max + 1 - param)
}

# Remove skipped elements (eg when Sample Size = 5,10,15,20...)
include = seq(1,(param.max - param.min + 1),iter)
tr.param_MSE = tr.param_MSE[include,]
te.param_MSE = te.param_MSE[include,]
dg.MSE     = dg.MSE[include,]
true.Model.MSE = true.Model.MSE[include,]

MSEs_wo_LOO_DPk = data.frame(SampleSize = dg.MSE$SampleSize, 
                  tr = tr.param_MSE, 
                  te = te.param_MSE, 
                  True.Model = true.Model.MSE$True.Model,
                  dg.Model = dg.MSE$True.Model)
```


```{r, echo = FALSE}
ggplot(MSEs_wo_LOO_DPk,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size",title = "MSE") + theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))

ggplot(MSEs_wo_LOO_DPk,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size", title = "MSE : ZOOMED") + ylim(0.1,15) +
  theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))

ggplot(MSEs_wo_LOO_DPk,aes(SampleSize)) + 
  geom_line(aes(y=tr.SG.Model,colour="Training SG")) +
  geom_line(aes(y=te.SG.Model,colour="Testing SG")) +
  geom_line(aes(y=True.Model,colour="True Model")) +
  geom_line(aes(y=dg.Model,colour="Gen Function")) +
  labs(y = "MSE",x="Sample Size", title = "MSE : ZOOMED") + ylim(0.1,2.5) +
  theme(legend.position = "bottom") + 
  scale_color_manual("", values = c("Testing SG" = "blue", "Training SG" = "black", "Gen Function" = "red","True Model" = "green"))
```

The below graph is attempting to solve why is Regular SG with LOO and SG without LOO so similar?
```{r}
plot(MSEs_LOO$SampleSize,MSEs_LOO$tr.SG.Model - MSEs_wo_LOO$tr.SG.Model, xlab = "Sample Size", ylab = "Train Set Difference", main = "SG Model Differences")
plot(MSEs_LOO$SampleSize,MSEs_LOO$te.SG.Model - MSEs_wo_LOO$te.SG.Model, xlab = "Sample Size", ylab = "Test Set Difference", main = "SG Model Differences")
```